### 2023-08-09 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

\section{Conclusions \label{sec:conclusion}}

>>>>

\section{Conclusions \label{sec:conclusion}}
In this work we used numerical simulations to examine the hydrodynamics of a multicomponent vesicle under strong confinement, which is a ubiquitous configuration in biology when a cell squeezes through a small channel. We refined the phase-field formulation in \citet{liu-mar-li-vee-low2017} with a new bending model that uses a sigmoidal function for the bending stiffness to retain positiveness in the bending modulus.
